Project Setup

### 2024-11-28 choose_license.qmd
Minor improvements and fixes

::: {.column-margin}
If you would like to choose a license not listed here, it should be appropriate for the type of work in question and be compatible with the dominant copyleft license in the respective community (see also @nte-silos). For software that's almost universally the (A)GPLv3 and for writing, image, audio, and video that's mostly the CC\ BY-SA\ 4.0. For data, no dominant copyleft license has emerged yet, so any of [ODbL\ 1.0](https://opendatacommons.org/licenses/odbl/summary/), [CDLA\ Sharing\ 1.0](https://cdla.dev/sharing-1-0/), and CC\ BY-SA\ 4.0 are acceptable.
:::

@@

One should be cautious about the restrictions of licenses applied to the following types of works:

>>>>

::: {.column-margin}
If you would like to choose a license not listed here, it should be appropriate for the type of work in question and be compatible with the dominant copyleft license in the respective community (see also @nte-silos). For software that's almost universally the (A)GPLv3 and for writing, image, audio, and video that's mostly the [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/). For data, no dominant copyleft license has emerged yet, so any of [ODbL\ 1.0](https://opendatacommons.org/licenses/odbl/summary/), [CDLA\ Sharing\ 1.0](https://cdla.dev/sharing-1-0/), and [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/) are acceptable.
:::

@@

One should take special care when applying license to the following types of works:

### 2024-11-28 intro.qmd
Minor improvements and fixes

## The importance of sharing

Suppose you are reading an article about a new imaging method to turn seismological data into subsurface images. The article describes the ideas that went into developing this method and presents a few examples to illustrate its superiority over previous approaches. You got interested and would like to apply this method to your own data. However, with only the article available, it could take months to come up with a working solution, if possible at all. This situation has been put aptly by @Buckheit1995, distilling an idea by Jon Claerbout:

@@

## Linking results and computations

@@

## Best practices

When creating the research compendium, there are a few things to consider [by @Arguillas2022, licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/)]:

>>>>

## The Importance of Sharing

Suppose you are reading an article about a new imaging method to turn seismological data into subsurface images. The article describes the ideas that went into developing this method and presents a few examples to illustrate its superiority over previous approaches. You got interested and would like to apply this method to your own data. However, with only the article available, it could take months to come up with a working solution, if possible at all. This situation has been put aptly by @Buckheit1995, distilling an idea by geophysicist Jon Claerbout:

@@

## Linking Results and Computations

@@

## Best Practices

When creating a research compendium, there are a few things to consider [by @Arguillas2022, licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/)]:

### 2024-11-28 setup.qmd
Minor improvements and fixes

Then, one can open an R session, by simply typing `R` into the terminal. Next, make sure that `getwd()` indicates that the working directory is `code-publishing-exercise`. If not, set it using `setwd("code-publishing-exercise")`. Then, initialize `renv`:

@@

::: {#tip-apaquarto .callout-tip}
#### Not a psychologist?

@@

::: {#tip-update-quarto .callout-tip}
If the PDF file cannot be created, try updating Quarto. It comes bundled with RStudio, however `apaquarto` sometimes requires more recent versions.
:::

>>>>

Then, one can open an R session by simply typing `R` into the terminal. Next, make sure that `getwd()` indicates that the working directory is `code-publishing-exercise`. If not, set it using `setwd("code-publishing-exercise")`. Then, initialize `renv`:

@@

::: {#tip-apaquarto .callout-tip}
#### Not a Psychologist?

@@

::: {#tip-update-quarto .callout-tip}
If the PDF file cannot be created, try updating Quarto. It comes bundled with RStudio, however, `apaquarto` sometimes requires more recent versions.
:::
